Untitled

### 2023-09-11 code/analysis_Redo.Rmd
measures of center

df.p %>% 
  filter(Year.y == Att.z) %>% 
  mutate(xcoor = xcoor / Radius, 
         ycoor = ycoor / Radius, 
         popcenter.x = popcenter.x / Radius, 
         popcenter.y = popcenter.y / Radius) %>% 
  #filter(Zip == "95076") %>% 
  ggplot(aes(x = xcoor, y = ycoor, color = ClinicType)) + 
  #geom_rect(aes(xmin = -SquareSide / 2, xmax = SquareSide / 2, ymin = -SquareSide / 2, ymax = SquareSide / 2), fill = "blue", alpha = 0.2, color = NA) + 
  geom_point(position=position_jitter(width=0.05, height=0.05)) + 
  xlim(-2, 2) + ylim(-2, 2)

>>>>

df.p %>% 
  filter(Year.y == Att.z) %>% 
  mutate(xcoor = xcoor / Radius, 
         ycoor = ycoor / Radius, 
         popcenter.x = popcenter.x / Radius, 
         popcenter.y = popcenter.y / Radius) %>% 
  filter(Zip == "43604") %>%  #43604
  ggplot(aes(x = xcoor, y = ycoor, color = ClinicType)) + 
  #geom_rect(aes(xmin = -SquareSide / 2, xmax = SquareSide / 2, ymin = -SquareSide / 2, ymax = SquareSide / 2), fill = "blue", alpha = 0.2, color = NA) + 
  geom_rect(aes(xmin = -1, xmax = 1, ymin = -1, ymax = 1), fill = "lightgrey", alpha = 0.2, color = NA) + 
  geom_point(position=position_jitter(width=0.05, height=0.05)) + xlim(-2, 2) + ylim(-2, 2) + 
  geom_point(aes(x = popcenter.x, y = popcenter.y), color = "green") #+ facet_wrap(~Zip)
